\LaTeX\ beamer template for Johns Hopkins University

### 2024-03-18 beamer/main.tex
updated repo

%%%%%%%%%%%%%%%%%%%%%%%% LaTeX CLASS AND THEME %%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[xcolor=dvipsnames,aspectratio=169]{beamer}
\useoutertheme[left]{sidebar}
\useinnertheme{rounded}
\usefonttheme[onlymath]{serif}                  % to use regular math font

@@

\usepackage[ruled]{algorithm2e}             % to manage algorithm environment
\usepackage[american]{babel}                % for different language typography

@@

%%%%%%%%%%%%%%%%%%%%%%%%% LaTeX MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%% END LaTeX MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[About Beamer]
{Beamer template for Johns Hopkins University}
%\subtitle{Template made on customized theme}
\author[Doe]{John Doe}

\institute[JHU] {
    Affiliated position \\
    Name of department or institute \\
    \includegraphics[width=0.35\textwidth, trim={0.6in 0.35in 0.6in 0.3in},clip]{JHU_logo.pdf}
}

\date[VLC 2021]{Very Large Conference, April 2021}
%%%%%%%%%%%%%%%%%%%%%%%%%%% END DOCUMENT INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begingroup
\makeatletter
\setbeamertemplate{navigation symbols}{}
\setlength{\hoffset}{-.4\beamer@sidebarwidth}
\makeatother
\begin{frame}[plain]
    \titlepage
\end{frame}
\endgroup

>>>>

\def\AspectRatio{169}                           % aspect ratio of the presentation
\def\FontPackage{helvet}                        % font package for presentation

\def\BaseFontSize{11pt}                         % base font size for beamer
\def\TitleFontSize{\Large}                      % title font size
\def\SubtitleFontSize{\large}                   % subtitle font size
\def\AuthorFontSize{\normalsize}                % author font size
\def\InstituteFontSize{\footnotesize}           % institute font size
\def\DateFontSize{\normalsize}                  % font size for the date on title page

\def\TitleLogoSize{0.35\textwidth}              % width of the logo on the title page

\def\FrameHeadHeight{1.0cm}                     % frame title height 
\def\SidebarWidth{0.75in}                       % width of the siebar

\def\FrameTitleFontSize{\Large}                 % frame title font size

%%%%%%%%%%%%%%%%%%%%%%%% LaTeX CLASS AND THEME %%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[xcolor=dvipsnames,aspectratio=\AspectRatio,\BaseFontSize]{beamer}
\useoutertheme[left]{sidebar}
\useinnertheme{rounded}
% \usefonttheme[onlymath]{serif}                  % to use regular math font

@@

\usepackage{helvet}
\usepackage[ruled]{algorithm2e}             % to manage algorithm environment
\usepackage[american]{babel}                % for different language typography

@@

%%%%%%%%%%%%%%%%%%%%% MATH SETTINGS AND MACROS %%%%%%%%%%%%%%%%%%%%%%%%

\allowdisplaybreaks[1]
\setcounter{MaxMatrixCols}{20}          % maximum columns in matrix = 20
\numberwithin{equation}{section}        % eqn no begins with section no
\newcommand{\dC}{$^{\circ}$C}           % degree celsius symbol
\newcommand{\vect}[1]{\mathbf{#1}}      % boldface for vectors and tensors
\DeclareMathOperator{\tr}{tr}           % trace of a matrix
\DeclareMathOperator{\divg}{div}        % divergence of vector and tensor
\DeclareMathOperator{\grad}{grad}       % gradient of vector and tensor

%% these are just some examples; add more macros for your custom symbols

%%%%%%%%%%%%%%%%%% END MATH SETTINGS AND MACROS %%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%% HIGHLIGHTING MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%% these are just some examples; add more macros

%%%%%%%%%%%%%%%%%%%% END HIGHLIGHTING MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[About Beamer]
{\LaTeX\ beamer template for Johns Hopkins University}
%\subtitle{Template made on customized theme}
\author[Doe]{John Doe}

\institute[JHU] {
    Affiliated position \\
    Name of department or institute \\
    \includegraphics[width=\TitleLogoSize,trim={0.6in 0.35in 0.6in 0.3in},clip]{JHU_logo.pdf}
}

\date[ALC 2024]{A Large Conference, March 2024}
%%%%%%%%%%%%%%%%%%%%%%%%%%% END DOCUMENT INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%% following code snippet is needed to remove the navigation symbols from the 
%%%% title slide as well as to bring the frame at the center by offsetting for 
%%% the sidebar.
\begingroup
\makeatletter
\setbeamertemplate{navigation symbols}{}            % removes page numbering
\setlength{\hoffset}{-.425\beamer@sidebarwidth}     %
\makeatother
\begin{frame}[plain]
    \titlepage
\end{frame}
\endgroup
